PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-02-22 main.tex
Discussion of circumplanetary accretion in conclusion

>>>>

To date, there have been no other studies of planetesimal accretion with such a large value of $\alpha$. However, a value of $\alpha = 1$ corresponds to the Roche limit of a three-body system, and so one might wonder this high-$\alpha$ accretion mode might be relevant for a circumplanetary system. There is a small collection of previous works which use N-body methods to examine in-situ satellitesimal accretion \citep{ida97, richardson00, ida20}. \citet{ida97} was able to form 1-2 large moon just exterior to the Roche limit, depending on the extent of the disk with very little satellitesimal material left over. The widest disk they modeled extended out to $\alpha = 0.5$. Qualitatively, this result is very similar to the short period planetesimal accretion mode observed in our simulations. \citet{ida20} modeled a much wider satellitesimal disk, which extends out to about $\alpha \approx 0.05$. Inside to the $\alpha = 0.1$ accretion boundary (which lies near $15 R_{U}$ in figure 1 of \citet{ida20}), bodies grow beyond the isolation mass, while the opposite is true on the other side of the boundary. In addition, a residual population of satellitesimals is still present beyond the boundary, which suggests that oligarchic growth is indeed operating on the far side.
